---
title: "ANOVA - Analysis of variance"
output: html_notebook
---
***

#### ***To confirm if the busiest days for Clerical staff are Wednesdays and Tuesdays***

***
#### Importing dataset
```{r}
anova = read.table("C:/Users/Supriya Khadake/Documents/Projects/ANOVA/Anova.txt", header = T)

#Checking first few records of the dataset
head(anova)
```
#### Statistical Description of the dataset
```{r}
summary(anova)
```
#### Structure of the dataset
```{r}
str(anova)
```
#### Assigning variables
```{r}
day = anova$DAY
hours = anova$HOURS
mail = anova$MAIL
cert = anova$CERT
acc = anova$ACC
change = anova$CHANGE
check = anova$CHECK
misc = anova$MISC
tickets = anova$TICKETS
```

***
#### Plotting Day against Hours
```{r}
plot(hours ~ day)
```
***Observe the box plot. Can you confirm that the hours in Tuesday is the highest? Why?***

- When variance is small it is easy to compare more than 2 groups based on median and mean value.

- Here for each group variance varies and is very large for few groups.

- We cannot simply read mean or median values and decide the highest hours for any day.

- We will have to take variance in consideration.

- for eg: median value for Tuesday is highest among all but not same with mean value and hence we cannot interpret based on this statistical description.

***

#### ANOVA F-tests the hypothesis:
- Null hypothesis: H0: Averages / Group mean value in hours by different days is equal

  -µ1 = µ2 = µ3 = µ4 = µ5 = µ6

- Alternate hypothesis: Ha: Not all the averages / group mean value in hours by different days are equal

Where,
  -µ1 = Group mean in hours by Friday
    
  -µ2 = Group mean in hours by Monday
    
  -µ3 = Group mean in hours by Saturday
    
  -µ4 = Group mean in hours by Tuesday
    
  -µ5 = Group mean in hours by Thursday
    
  -µ6 = Group mean in hours by Wednesday

```{r}
anova_model = lm(hours ~ day)
summary(anova_model)
```
***
Based on F-statistic: 4.227 and 5 and 46 DF with p-value: 0.003033 < 0.05

We reject Null hypothesis and help manager with this saying that the group means in hours by different days are not same

***
- Groups which are not significant

Monday, Saturday and Thursday coefficient have p-value more than 0.05 hence they are not significant

And as these groups are not significant, then the corresponding coefficient can be assumed equal to zero

- Groups which are significant

Tuesday and Wednesday coefficient have p-value less than 0.05 hence they are significant

In particular, the group mean value in hours involved in Tuesday is 20.531 higher than the group mean value in hours involved in Friday.
and the group mean value in hours involved in Wednesday is 23.342 higher than the group mean value in hours involved in Friday

***